The Iterative Signature Algorithm

### 2009-05-14 isa2/inst/doc/ISA_tutorial.Rnw
isa package renamed to isa2.

To run the typical ISA work flow with default parameters on your data
matrix, just load the \Rpackage{isa} package and call the
\Rfunction{isa} function with your matrix as the single argument. The
return value of \Rfunction{isa} is a named list, the members
\texttt{rows} and \texttt{columns} contain the biclusters ISA have
found. Every bicluster is given by a pair of columns from
\texttt{rows} and \texttt{columns} (i.e. the first columns define the
first bicluster, etc.) and the elements the biclusters are the
non-zero elements in the columns of \texttt{rows} and
\texttt{columns}.

@@

Fig.~\ref{fig:twoclusters} shows possibly the simplest
example of a (rather artificial) data matrix with very strong modular
structure. It is a $20\times 20$ matrix and has two correlated blocks,
each of them of size $10\times 10$.
\begin{figure}
<<toymatrix,echo=FALSE,fig=TRUE,width=6,height=3>>=
library(isa)
library(Matrix)
data <- data2 <- isa.in.silico(20,20,2,10,10)[[1]]
perm1 <- sample(seq_len(nrow(data)))
data2 <- data2[perm1,]
perm2 <- sample(seq_len(ncol(data)))
data2 <- data2[,perm2]

@@

Let us see an example. We load the \Rpackage{isa} generate some in
silico data with the \Rfunction{isa.in.silico} function first:
<<insilico,cache=TRUE>>=
data <- isa.in.silico(200,200,2,50,50)[[1]]
@
The function call above generates the data matrix in
Fig.~\ref{fig:twoclusters}. The first two arguments define the size of
the data matrix ($200\times 200$), the third the number of modules (two)
and the fourth and fifth give the size of the modules, both are
$50\times 50$ submatrices in this case. By default
\Rfunction{isa.in.silico} creates non-overlapping modules with some
background noise.

@@

\bibitem[Cs\'ardi, 2009]{isapackage}
Cs\'ardi, G. (Apr 1, 2009).
\newblock {\em isa: The Iterative Signature Algorithm}.
\newblock R package version 0.1.

>>>>

To run the typical ISA work flow with default parameters on your data
matrix, just load the \Rpackage{isa2} package and call the
\Rfunction{isa} function with your matrix as the single argument. The
return value of \Rfunction{isa} is a named list, the members
\texttt{rows} and \texttt{columns} contain the biclusters ISA have
found. Every bicluster is given by a pair of columns from
\texttt{rows} and \texttt{columns} (i.e. the first columns define the
first bicluster, etc.) and the elements the biclusters are the
non-zero elements in the columns of \texttt{rows} and
\texttt{columns}.

@@

Fig.~\ref{fig:twoclusters} shows possibly the simplest
example of a (rather artificial) data matrix with very strong modular
structure. It is a $20\times 20$ matrix and has two correlated blocks,
each of them of size $10\times 10$.
\begin{figure}
<<toymatrix,echo=FALSE,fig=TRUE,width=6,height=3>>=
library(isa2)
library(Matrix)
data <- data2 <- isa.in.silico(20,20,2,10,10)[[1]]
perm1 <- sample(seq_len(nrow(data)))
data2 <- data2[perm1,]
perm2 <- sample(seq_len(ncol(data)))
data2 <- data2[,perm2]

@@

Let us see an example. We load the \Rpackage{isa2} generate some in
silico data with the \Rfunction{isa.in.silico} function first:
<<insilico,cache=TRUE>>=
data <- isa.in.silico(200,200,2,50,50)[[1]]
@
The function call above generates the data matrix in
Fig.~\ref{fig:twoclusters}. The first two arguments define the size of
the data matrix ($200\times 200$), the third the number of modules (two)
and the fourth and fifth give the size of the modules, both are
$50\times 50$ submatrices in this case. By default
\Rfunction{isa.in.silico} creates non-overlapping modules with some
background noise.

@@

\bibitem[Cs\'ardi, 2009]{isapackage}
Cs\'ardi, G. (Apr 1, 2009).
\newblock {\em isa2: The Iterative Signature Algorithm}.
\newblock R package version 0.1.
